GDPR: Is non-compliance profitable for Meta Platforms, Inc.?

### 2023-06-10 docs/research/LaTeX/research.tex
Add first 3 figures and edit method

\documentclass[12pt, a4paper]{article}
\usepackage{indentfirst}
\usepackage{graphicx}
\usepackage{url}
\graphicspath{{images/}}
\title{GDPR: Is non-compliance profitable for Meta Platforms, Inc.?}
\author{Stoyan L. Kostadinov}
\date{June 2023}
\begin{document}
\maketitle

@@

GDPR, Facebook, Meta, profit, non-compliance, big tech, privacy, financial
impact

@@

One of those companies is \textit{Meta Platforms, Inc.} (formerly
\textit{Facebook, Inc.}), which has been fined numerous times for GDPR
violations\cite{mrevzar2023analysis}. This has raised questions about the
financial impact of GDPR non-compliance from \textit{Meta} and whether it is
profitable for the company to continue violating the regulation.

@@

All numerical data about \textit{Meta Platforms, Inc.} has been gathered from
the official \textit{Meta Investor Relations} website\cite{fbMetaFinancials}.

GDPR fines imposed on \textit{Meta Platforms, Inc.} have been gathered from the
\textit{GDPR Enforcement Tracker}
website\cite{enforcementtrackerGDPREnforcement}.

This research is following the protocol of \textit{Prisma flowchart} for
systematic reviews\cite{prismaFlowchart}.

\textit{Google Scholar} was used to search for articles containing the keywords
above. The first 360 results were considered. The articles were filtered by
relevance following their titles and 60 were considered. The abstracts of the 60
articles were read and X were considered
% TODO: Describe flowchart with sentences above here TODO: Put numbers and add
% flowchart here as Figure 1

@@

\begin{itemize}
    \item Articles published in English
    \item Articles published between 2018 and 2023
    \item Articles that discuss GDPR
    \item Articles that discuss Meta Platforms, Inc.
    \item Data between 2021 and 2023
\end{itemize}

@@

\begin{itemize}
    \item Articles published in languages other than English
    \item Articles published before 2018
    \item Articles that do not discuss GDPR
    \item Articles that do not discuss Meta Platforms, Inc.
    \item Articles that discuss about ethics
    \item Data before 2021
\end{itemize}

@@

@@

% Investigate the costs incurred by Meta Platforms in legal proceedings related
% to GDPR non-compliance. This includes expenses associated with hiring legal
% counsel, litigation, settlement agreements, and any ongoing legal obligations.
% Analyze the financial impact of these legal expenses on the company's
% profitability.

@@

@@

@@

>>>>

\documentclass[12pt, a4paper]{article}
\usepackage{indentfirst}
\usepackage{graphicx}
\usepackage{url}
\usepackage[font=footnotesize,labelfont=bf]{caption}
\graphicspath{{images/}}
\title{GDPR: Is non-compliance profitable for Meta Platforms, Inc.?}
\author{Stoyan L. Kostadinov}
\date{June 2023}
\begin{document}
\maketitle

@@

GDPR, Facebook, Meta, profit, non-compliance, privacy, financial impact

@@

One of those companies is \textit{Meta Platforms, Inc.} (formerly
\textit{Facebook, Inc.}), which has been fined numerous times for GDPR
violations\cite{mrevzar2023analysis}. This has raised questions about the impact
of GDPR on \textit{Meta's} performance.

@@

All numerical data about \textit{Meta Platforms, Inc.} has been gathered from
the official \textit{Meta Investor Relations} website\cite{fbMetaFinancials} -
\textbf{Balance Sheet}, \textbf{Income Statement} and \textbf{Form 10-Q}.

GDPR fines imposed on \textit{Meta Platforms, Inc.} have been gathered from the
\textit{GDPR Enforcement Tracker}
website\cite{enforcementtrackerGDPREnforcement} and filtered to include fines
imposed on their family of applications (\textbf{\textit{Facebook}},
\textbf{\textit{WhatsApp}}, \textbf{\textit{Instagram}}) and
\textbf{\textit{Meta Platforms, Inc.}} itself.

@@

\begin{itemize}
    \item Articles published in English
    \item Articles published between 2018 and 2023
    \item Articles that discuss GDPR
    \item Articles that discuss Meta Platforms, Inc.
    \item Data between 2018 and 2023
\end{itemize}

@@

\begin{itemize}
    \item Articles published in languages other than English
    \item Articles published before 2018
    \item Articles that do not discuss GDPR
    \item Articles that do not discuss Meta Platforms, Inc.
    \item Articles that discuss about ethics
    \item Data before 2018
\end{itemize}

@@

% TODO: cite

\begin{figure}[h]
    \centering
    \includegraphics[width=1.00\textwidth]{monetarial-amount-of-gdpr-fines}
    \caption{Monetarial amount of fines issued to Meta Platforms, Inc.(in millions of \$)}
    \label{fig:amount-of-gdpr-fines}
\end{figure}

\begin{figure}[h]
    \centering
    \includegraphics[width=1.00\textwidth]{violations-by-article}
    \caption{Number of violations by GDPR article}
    \label{fig:violations-by-article}
\end{figure}

\begin{figure}[h]
    \centering
    \includegraphics[width=1.00\textwidth]{net-income}
    \caption{Net Income of Meta Platforms, Inc.(in billions of \$)}
    \label{fig:net-income}
\end{figure}

@@

% Investigate the costs incurred by Meta Platforms in legal proceedings related
% to GDPR non-compliance. This includes expenses associated with hiring legal
% counsel, litigation, settlement agreements, and any ongoing legal obligations.
% Analyze the financial impact of these legal expenses on the company's
% profitability.
% https://www.law.com/corpcounsel/2021/11/24/as-regulators-hover-meta-expands-legal-department/

% https://www.law.com/corpcounsel/2022/11/10/meta-cuts-hit-legal-department-slamming-brakes-on-its-explosive-growth/?slreturn=20230510140111

% https://www.google.com/search?channel=fs&client=ubuntu&q=glasdoor+meta+lawyer+salary

@@

% advertising data

@@

% https://d18rn0p25nwr6d.cloudfront.net/CIK-0001326801/5fb5d0ea-c2c7-46f0-a26a-656df1673fac.pdf
% page 14 revenue from europe page 42 41 37 and onwards

@@

% hard to assess
